\documentclass[a4paper,12pt]{article}
\input{wsconfig.tex}  % This loads the magic package =)

\title{
    LaTeX Example Document: \\
    \large{How to create a nice paper} \\
}

\author{
     \small{Person One \textit{<personone@somemail.com>}} \\
     \small{Person Two \textit{<persontwo@somemail.com>}} \\
     \small{Last Person \textit{<lastperson@somemail.com>}} \\
}

\date{November 2022}

\begin{document}
\maketitle

\begin{abstract}
    This is a very simple document, intended to serve as a starting
    point for those who want to create a LaTeX paper. As a simple article,
    you can just replace the sections you plan to use, delete the
    ones you wont, and configure the settings and references as
    you wish.

    \vspace{1em}
    \noindent\textbf{Keywords:} LaTeX, Simple, Template
\end{abstract}

\section*{Acronyms}
\begin{acronym}[ICANN]
    \input{acronyms.tex}  % <== This loads a separate list of acronyms
\end{acronym}

\section{Introduction}
Hello, world! This is a very simple document for beginners. It will not
contain many different structures and resources, as it is intended
to be simple, but you can search for further examples on the Internet. For example,
the LaTeX Manual for Authors \cite{LaTeX2020} contains plenty of good tips.

With LaTeX it is easy to cite articles, like this one written by \textcite{SomeAuthor2022},
or even a book, like this \cite{Genius1801}. Try changing some options in the configuration
file and check out the results. Also, acronyms like \ac{i3e} and \ac{smart} are an easy task.
Happy writing!

\newpage
\printbibliography[heading=bibnumbered,title=References]

\end{document}
